si: code and prose exploring Spatial Interaction models

### 2022-06-13 README.qmd
Document

To dive straight into using {simodels} to develop SIMs, see the [`si` Get started vignette](https://robinlovelace.github.io/simodels/articles/si.html).

>>>>

To dive straight into using {simodels} to develop SIMs, see the [Get started vignette](https://robinlovelace.github.io/simodels/articles/simodels.html).
